Click chemistry reveals an alternate mechanism for HPII catalase

### 2018-02-21 bb494/manuscript.tex
add errthing

5th para
- our ncAA experiment, and how if we can destroy the dielectric variance of catalase via AA addition
- how ncAAs are incorporated

Catalase is an enzyme which catalyzes the breakdown of hydrogen peroxide into water and oxygen gas. This is an important detoxification reaction, since hydrogen peroxide is a reactive toxin generated by several biological processes. Catalase is a tetrameric protein which uses a heme group in its active site to facilitate the breakdown of hydrogen peroxide.

@@

>>>>

Catalase is an enzyme which catalyzes the breakdown of hydrogen peroxide into water and oxygen gas. This is an important detoxification reaction, since hydrogen peroxide is a reactive toxin generated by several biological processes. Catalase is a tetrameric protein which uses a heme group in its active site to facilitate the breakdown of hydrogen peroxide. The protein is

Catalase's activity is nearly diffusion-limited \cite{kcatkm, difflimit}. This rate suggests that nearly every step in the substrate-enzyme interaction is optimized for speed. Understanding these optimizations is good because __________. Catalase has a variety of interesting optimizations in funneling substrate into its active pocket. The enzyme has a number of high-H2O2-residency surface residues near its active channel, which are believed to concentrate the substrate near the entrance to the active channel \cite{concentrateh2o2}. The active channel itself seems optimized to maximize substrate flow, to the point that mutagenesis to open the channel decreases enzyme activity \cite{substrateflow}. The channel seems to be capable of selecting the molecules which enter it using a patch of hydrophobic residues which are situated to preferentially pass the bulkier H2O2 \cite{molecularruler}. Even the directionality of substrate within the channel seems to be controlled: one channel is used for substrate entrance, and the other for product exit \cite{lateralchannel}. An new finding is that catalase might control not just the presence of catalase, but even its orientation as it enters the active site. It is believed that an electric field from a negative Asn residue to the positive heme acts to orient the H2O2 dipole, positioning the molecule such that it enters the active site at an angle ideal for reacting \cite{electricpotential}. It is this orientation that we hope to explore in this research.

@@

The Catalase-Hydrogen Peroxide System, Suggett
Km: 1.1M,
kcat/Km: 6.6*10^7/M/s
